### 2020-02-12 paper/results.tex

Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
is relatively low when compared to Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
elements for all three cases reach the equilibrium state after $\approx$ $30$ 
years (see Figure~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC}).

@@

Even after 30 years of operation, the total temperature coefficient of 
reactivity remains relatively large and negative (in the range between $-2.59$ 
and $-5.06$ pcm/K) compared to the conventional \gls{PWR}, which has 
temperature coefficient of about $-1.71$ $pcm/^{\circ}F\approx -3.08$ $pcm/K$ 
\cite{forget_integral_2018}, and allows excellent reactor stability and 
control. The additional analysis must be performed taking graphite moderator 
density change and linear thermal expansion into account, but material 
properties for the SD-TMSR graphite are not available in published literature. 
Relatively well-studied reactor graphite (e.g., AXQ graphite 
\cite{robertson_conceptual_1971}) can be considered as a candidate for the 
SD-TMSR concept.

>>>>

Figure~\ref{fig:inventoryPu_TRUCCC} shows that the mass of Pa in the fuel salt 
is relatively low when compared with Pa mass in the $^{233}$U case (Figure~\ref{fig:inventoryCCCC}). Major 
elements for all three cases reach the equilibrium state after $\approx$ $30$ 
years (see Figure~\ref{fig:inventoryCCCC} and~\ref{fig:inventoryPu_TRUCCC}).

@@

Even after 30 years of operation, the total temperature coefficient of 
reactivity remains relatively large and negative (in the range between $-2.59$ 
and $-5.06$ pcm/K) compared with the conventional \gls{PWR}, which has 
temperature coefficient of about $-1.71$ $pcm/^{\circ}F\approx -3.08$ $pcm/K$ 
\cite{forget_integral_2018}, and allows excellent reactor stability and 
control. The additional analysis must be performed taking graphite moderator 
density change and linear thermal expansion into account, but material 
properties for the SD-TMSR graphite are not available in published literature. 
Relatively well-studied reactor graphite (e.g., AXQ graphite 
\cite{robertson_conceptual_1971}) can be considered as a candidate for the 
SD-TMSR concept.
